### 2017-02-26 2017mergingmerges/section/02-Processes.tex
Kill commented out stuff in S1 S2 that we've already handled

%!TEX root = ../Main.tex
\section{Processes, Machines, Combinators and Operators}
\label{s:Processes}

@@

% -----------------------------------------------------------------------------
\subsection{Fusion}
Our fusion algorithm takes two process state machines and produces a new one that computes the outputs of both. For example, suppose we need a single machine that computes the outputs of the first two combinators of our @uniquesUnion@ example back in \S\ref{s:Introduction}. The result will be a machine that computes the result of both the @group@ and @merge@ as if they were executed concurrently, where the first input stream of the @merge@ is the same as the input stream of the @group@. For ease of comparison we will assume the parameters in each combinator are instantiated by arguments with the same names.

@@

Overall, our fusion algorithm has taken two separate processes that we once imagined to be running concurrently, and has produced a single sequental result process that implements both. We have chosen a \emph{specific sequential order} in which to interleave instructions that implement both original processes. As with the Flow Fusion system of \cite{lippmeier2013data} we have performed the job of a concurrent scheduler at compile time. However, in contrast to Flow Fusion and similar systems, we do not need to organize statements into a fixed \emph{loop anatomy}, we simply merge them as they are. This allows us to implement a wider range of processes, including ones with nested loops that work on segmented streams, which we discuss further in \S\ref{s:FutureWork}.

@@

% BL: This is too much low level detail at this point, we need more intuition.

@@

>>>>

%!TEX root = ../Main.tex

% -----------------------------------------------------------------------------
\section{Processes, Machines, Combinators and Operators}
\label{s:Processes}

@@

% -----------------------------------------------------------------------------
\subsection{Fusion}

Our fusion algorithm takes two process state machines and produces a new one that computes the outputs of both. For example, suppose we need a single machine that computes the outputs of the first two combinators of our @uniquesUnion@ example back in \S\ref{s:Introduction}. The result will be a machine that computes the result of both the @group@ and @merge@ as if they were executed concurrently, where the first input stream of the @merge@ is the same as the input stream of the @group@. For ease of comparison we will assume the parameters in each combinator are instantiated by arguments with the same names.

@@

Overall, our fusion algorithm has taken two separate processes that we once imagined to be running concurrently, and has produced a single sequental result process that implements both. We have chosen a \emph{specific sequential order} in which to interleave instructions that implement both original processes. As with the Flow Fusion system of \citet{lippmeier2013data} we have performed the job of a concurrent scheduler at compile time. However, in contrast to Flow Fusion and similar systems, we do not need to organize statements into a fixed \emph{loop anatomy}, we simply merge them as they are. This allows us to implement a wider range of processes, including ones with nested loops that work on segmented streams, which we discuss further in \S\ref{s:FutureWork}.

@@

@@

% -----------------------------------------------------------------------------
% BL: This is too much low level detail at this point, we need more intuition.
